---
title: "Sarita visualization app"
author: "Q. Huynh, Blue Matter"
date: "2026-01-07"
format: html
server: shiny
---

```{r}
#| context: setup
#| include: FALSE

knitr::opts_chunk$set(
  echo = FALSE
)

### Install packages ----
pkg <- c("rmarkdown", "shiny", "shinyWidgets", "dplyr", "ggplot2", "here", "ggborderline", "reshape2")
sapply(pkg, function(i) {
  if (!i %in% installed.packages()) install.packages(i)
})

library(shiny)
library(shinyWidgets)
library(tidyverse)

### Import functions ----
fn_file <- "99-Sarita-results-functions.R"

if (file.exists(here::here(fn_file))) {
  source(here::here("99-Sarita-results-functions.R"))
} else {
  fn_file <- file.path(tempdir(), "99-Sarita-results-functions.R")
  download.file(
    "https://raw.githubusercontent.com/Blue-Matter/WCVI_Chinook/refs/heads/main/99-Sarita-results-functions.R",
    fn_file
  )
  source(fn_file)
}
figure_height <- 600
```


```{r}
#| context: data
#| include: false

### Grab array and convert to data frame, download if necessary ----
if (dir.exists(here::here("tables")) && file.exists(here::here("tables/Sarita_app_results.rds"))) {
  output <- readRDS(here::here("tables/Sarita_app_results.rds")) 
} else {
  file_name <- file.path(tempdir(), "Sarita_app_results.rds")
  download.file(
    "https://github.com/Blue-Matter/WCVI_Chinook/raw/refs/heads/main/tables/Sarita_app_results.rds",
    file_name
  )
  output <- readRDS(file_name)
}

var_plot <- c("Egg (10^6)", "Outmigrating juvenile (10^5)", #"Hatchery Release (10^5)",
              "Preterminal catch", "Mature Return", "Terminal catch", "In-river Return",
              "Brood", "In-river Catch", "Natural Spawners")
val <- reshape2::melt(output$State) %>%
  mutate(var_name = factor(var_name, var_plot))


var_plot_hatchery <- c("Releases", "pHOSeff", "PNI")
if (!is.null(output$Hatchery)) {
  val_hatchery <- reshape2::melt(output$Hatchery) %>%
    mutate(var_name = factor(var_name, var_plot_hatchery))
} else {
  val_hatchery <- NULL
}

```

This webpage presents simulation results from the application of candidate management strategies for Sarita Chinook across alternative plausible scenarios. 
Interactive results are intended to efficiently share comprehensive results with a working group when static figures may be cumbersome to distribute. 
Figures below show outcomes from user selected scenario, management option, and subset of simulations.

This document is rendered in Quarto and made interactive using Shiny.


## Filter results 

Select one population scenario (A-E) and one management strategy (1-9).

```{r}
#| label: input-scenario
inputPanel(
  selectInput("OM", label = "Scenario",
              choices = unique(val$Scenario), width = "200%"),
  
  selectInput("MP", label = "Management option",
              choices = unique(val$scenario), width = "200%")
)
```

::: {.panel-tabset}

### Spaghetti plot 

#### All simulations

```{r}
#| label: fig-spaghetti
#| fig-cap: "Time series lineplots of state variables for all simulations (grey lines) with annual median in blue."
plotOutput("spaghetti", height = figure_height)
```

```{r}
#| label: fig-spaghetti-hatchery
#| fig-cap: "Time series lineplots of hatchery-specific state variables for all simulations (grey lines) with annual median in blue."
plotOutput("spaghetti_hatchery", height = 0.5 * figure_height)
```

#### All simulations, by origin

```{r}
#| label: fig-spaghetti-origin
#| fig-cap: "Time series lineplots of state variables by fish origin (colours) for all simulations (thin lines) with annual medians in solid lines."
plotOutput("spaghetti_origin", height = figure_height)
```

#### Subset of simulations

```{r}
#| label: input-spaghetti-sim
inputPanel(
  #shinyWidgets::pickerInput( # Doesn't work in quarto
  #  "Sim_spaghetti", label = "Simulation Number (up to 8 total)",
  #  choices = unique(val$Simulation),
  #  selected = seq(1, min(val$Simulation, 3)),
  #  multiple = TRUE
  #)
  
  selectInput(
    "Sim_spaghetti", label = "Simulation Number (up to 8 total, select and delete to remove choices)",
    choices = unique(val$Simulation),
    selected = seq(1, min(val$Simulation, 3)),
    multiple = TRUE,
    width = "400px"
  )
)
```

```{r}
#| label: fig-spaghetti-sim
#| fig-cap: "Time series lineplots of state variables by a subset of simulations selected above."
plotOutput("spaghetti_subset", height = figure_height)
```

### Barplots 

```{r}
#| label: input-barplot-sim
inputPanel(
  selectInput("Sim_barplot", label = "Simulation Number",
              choices = unique(val$Simulation))
)
```

```{r}
#| label: fig-barplot
#| fig-cap: "Time series stacked barplots of state variables by fish origin for an individual simulation."
plotOutput("barplot", height = figure_height)
```







```{r}
#| context: server

val_plot_origin <- reactive({
  dplyr::filter(
    val,
    Scenario == input$OM,
    scenario == input$MP,
    ifelse(var_name == "Outmigrating juvenile (10^5)", Year > 1, Year < max(.data$Year))
  )
})

val_plot_hatchery <- reactive({
  dplyr::filter(
    val_hatchery,
    Scenario == input$OM,
    scenario == input$MP,
    ifelse(var_name == "Releases", Year > 1, Year < max(.data$Year))
  )
})

val_plot <- reactive({
  val_plot_origin() %>%
    summarise(value = sum(value, na.rm = TRUE), .by = c(Year, var_name, Scenario, scenario, Simulation))
})

output$spaghetti <- renderPlot({
  plot_spaghetti(val_plot(), OM_name = input$OM, MP_name = input$MP)
}, res = 100, height = figure_height)

output$spaghetti_hatchery <- renderPlot({
  plot_spaghetti(val_plot_hatchery(), OM_name = input$OM, MP_name = input$MP)
}, res = 100, height = 0.5 * figure_height)

output$spaghetti_origin <- renderPlot({
  plot_spaghetti(val_plot_origin(), OM_name = input$OM, MP_name = input$MP, by_origin = TRUE, alpha = 0.1)
}, res = 100, height = figure_height)

output$spaghetti_subset <- renderPlot({
  plot_spaghetti(val_plot(), sims = input$Sim_spaghetti, OM_name = input$OM, MP_name = input$MP)
}, res = 100, height = figure_height)

val_plot_origin_sim <- reactive({
  dplyr::filter(
    val_plot_origin(),
    Simulation == input$Sim_barplot
  )
})

output$barplot <- renderPlot({
  val_plot_origin_sim() %>%
    ggplot(aes(Year, value)) +
    facet_wrap(vars(var_name), scales = "free_y") +
    geom_col(colour = "black", linewidth = 0.1, width = 1, alpha = 0.75, aes(fill = Origin)) +
    expand_limits(y = 0) +
    theme(strip.background = element_blank(), legend.position = "bottom") +
    labs(y = NULL, fill = NULL, title = input$OM, subtitle = input$MP, caption = paste("Simulation", input$Sim_barplot))
  
}, res = 100, height = figure_height)
```


